---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

The source data for this project is named `activity.zip` and can be
found in the working directory for the project. The first step to
perform for loading to unzip this file to extract the `activity.csv`
file into the working directory:

```{r}
unzip("activity.zip")
```

The second step is to load the extracted `activity.csv` file into a data
frame and see what we have:

```{r}
source_data <- read.csv("activity.csv", stringsAsFactors=FALSE)
str(source_data)
```

Create an attribute for timestamps for each entry based on the date and
interval attributes.

```{r}
source_data$timestamp <- strptime(paste(
                                    source_data$date,
                                    sub("(\\d{2})(\\d{2})",
                                        "\\1:\\2",
                                        sprintf("%04d", source_data$interval)
                                    )
                                  ),
                                  "%Y-%m-%d %R")

str(source_data)
```

## What is mean total number of steps taken per day?

Calculate the total number of steps taken per day:

```{r}
library(plyr)
steps_per_day <- ddply(source_data, "date", summarise, total_steps=sum(steps))
summary(steps_per_day)
```

Plot a histogram of steps per day:

```{r}
hist(steps_per_day$total_steps)
```




## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
